Computing Entropies With Nested Sampling

### 2017-05-24 paper/ms.tex
Bernardo
Back to Euclidean distances

>>>>

Continuous hypothesis spaces are commonly used in practice. Suppose
$\x$ has probability density $f(\x)$. The algorithm actually estimates
\begin{align}
h &= \int f(\x) \int f(\x')
            \log \left[ P(d(\x', \x) < \epsilon | \x) \right]
                        \, d\x' \, d\x.
\end{align}
If we actually want the differential
entropy
\begin{align}
h_{\x} &= -\int f(x) \log f(x) \, dx
\end{align}
we can use the fact that density equals mass divided
by volume. Assume $\epsilon$ is small, so that
\begin{align}
P(d(\x', \x) < \epsilon | \x)
    &\approx
    f(\x) \int_{d(\x', \x) < \epsilon} \, d\x'\\
    &= f(\x) \, V
\end{align}
where $V$ is the volume of the region where $d(\x', \x) < \epsilon$.

If the distance function $d(\x', \x)$ is chosen to be Euclidean,
the constraint $d(\x', \x) < \epsilon$ corresponds to a ball in the space
of possible $\x'$ values.
The log-volume of a ball of radius $\epsilon$ in $n$ dimensions is
\begin{align}
\log V(\epsilon; n) &= \frac{n}{2}\log \pi
                        - \log \Gamma\left(\frac{n}{2} + 1\right)
                        + n \log \epsilon,
\end{align}
and provides the conversion factor between the differential entropy and
the entropy actually computed from the algorithm.
